\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2012-07-07 doc/USER_MANUAL/manual_SPECFEM3D.tex
updated the manual

For a detailed introduction to the SEM as applied to regional
seismic wave propagation, please consult \citet{KoVi98,KoTr99,ChKoViCaVaFe07,TrKoLi08,PeKoLuMaLeCaLeMaLiBlNiBaTr11} and
in particular \citet{KoLiTrSuStSh04,LeKoHuTr09,LeChKoHuTr09,LeChLiKoHuTr08,GoAmTaCaSmSaMaKo09,WiKoScTr04}.
A detailed theoretical analysis of the dispersion
and stability properties of the SEM is available in \citet{Coh02}, \citet{DeSe07}, \citet{SeOl07} and \citet{SeOl08}.\\

>>>>

For a detailed introduction to the SEM as applied to regional
seismic wave propagation, please consult \citet{PeKoLuMaLeCaLeMaLiBlNiBaTr11,TrKoLi08,KoVi98,KoTr99,ChKoViCaVaFe07} and
in particular \citet{LeKoHuTr09,LeChKoHuTr09,LeChLiKoHuTr08,GoAmTaCaSmSaMaKo09,WiKoScTr04,KoLiTrSuStSh04}.
A detailed theoretical analysis of the dispersion
and stability properties of the SEM is available in \citet{Coh02}, \citet{DeSe07}, \citet{SeOl07} and \citet{SeOl08}.\\
